---
title: "Men-and-Me-Too-Movement-Survey"
author: "Mai Le"
date: "5/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(dplyr) #grouping and manipulating data
library(ggplot2) #data visualizations
library(tidyr) #cleaning data
library(RColorBrewer) #color palettes
```

```{r, message=FALSE, warning=FALSE}
response <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/masculinity-survey/raw-responses.csv",
                     header=TRUE, stringsAsFactors = FALSE)
```

##2.1 Reproduct figures and charts in the article with separate analysis for Straight and Gay/Bixexual men

###2.1.1 Does society put unhealthy pressure on men?
```{r, message=FALSE, warning=FALSE}
# Select only Straight and Gay/Bisexual respondents
selected <- c("Straight", "Gay/Bisexual")
orientation2 <- response[response$orientation %in% selected,]

# Graph 1. stacked bar plot
p1 = ggplot(orientation2) + 
  geom_bar(aes(x=orientation, fill=q0005, label=paste0(q0005)), position = "fill") + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position =  "top") +
  scale_y_continuous()

p1 + labs(title ="Do you think that society puts pressure on men in a way that is unhealthy or bad for them?", x = "Sexual Orientation", y = "Response Composition") + scale_fill_brewer(palette ="Spectral")

```

###2.1.2 What do you worry about on a daily or near-daily basis?
```{r,message=FALSE,warning=FALSE}
# question 8 variables
raw8 = orientation2 %>% select(starts_with('q0008'))

# go to wide to long format
str(long)
str(raw8)
1615*12 # right size

# counts for each response 
tab1 = long %>% group_by(value) %>% count
#filter out "not selected" response, which is the most common
tab1 = tab1 %>% filter(n < 10000)
#convert q0026 into factor
tab1$q0026 <- as.factor(tab1$q0026)
p2.1.2 = ggplot(tab1, aes(x = reorder(value,n), y = 100*n/nrow(raw8)),position="fill") + 
        geom_bar(stat = 'identity') + 
        coord_flip()

p2.1.2 +labs(title ="What do you worry about on a daily or near-daily basis?", y = "Response composition", x = "Responses")
```

###2.1.4 How often do you pay on a date? 
```{r, message=FALSE, warning=FALSE}
p4 = ggplot(orientation2) + 
  geom_bar(aes(x=q0018, fill=orientation), position = "fill") +
  coord_flip() +
  theme_minimal() +
  theme(legend.position =  "top")

p4 + labs(title ="How often do you try to be the one who pays on a date? ", x = "Response", y = "Response Composition") + scale_fill_brewer(palette ="Dark2")
```



## 2.2 Reproduct figures and charts in the article with separate analysis for White and Nonwhite men

###2.2.1 Does society put unhealthy pressure on men?
```{r, message=FALSE, warning=FALSE}
p2.1 = ggplot(orientation2) + 
  geom_bar(aes(x=race2, fill=q0005, label=paste0(q0005)), position = "fill") + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position =  "top")

p2.1 + labs(title ="Do you think that society puts pressure on men in a way that is unhealthy or bad for them?", x = "Race", y = "Response Composition") + scale_fill_brewer(palette ="Set2")

```

###2.2.4 How often do you pay on a date? 
```{r, message=FALSE, warning=FALSE}
p2.4 = ggplot(orientation2) + 
  geom_bar(aes(x=q0018, fill=race2), position = "fill") +
  coord_flip() +
  theme_minimal() +
  theme(legend.position =  "top")

p2.4 + labs(title ="How often do you try to be the one who pays on a date? ", x = "Response", y = "Response composition") + scale_fill_brewer(palette ="Set3")
```

##2.3
As a man, would you say you think about your behavior at work differently in the
wake of #MeToo?
```{r,message=FALSE,warning=FALSE}
#Remove respondents NA responses
noNA <- response %>% na.omit

#stacked bar plot
p2.3.1 = ggplot(noNA) + 
  geom_bar(aes(x=q0024, fill=q0015), position = "fill") + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "top") 

p2.3.1 + labs(title ="As a man, would you say you think about your behavior at work differently in the wake of #MeToo?", x = "Relationship Status", y = "Response Composition") + scale_fill_brewer(palette ="Dark2")
```


Do you typically feel as though you’re expected to make the first move in romantic
relationships?
```{r,warning=FALSE, message=FALSE}
#stacked bar plot
p2.3.2 = ggplot(noNA) + 
  geom_bar(aes(x=q0024, fill=q0015), position = "fill") + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "top") 

p2.3.2 + labs(title ="Do you typically feel as though you’re expected to make the first move in romantic relationships?", x = "Relationship Status", y = "Response Composition") + scale_fill_brewer(palette ="Set2")
```

How much have you heard about the #MeToo movement?
```{r,warning=FALSE, message=FALSE}
#stacked bar plot
p2.3.2 = ggplot(noNA) + 
  geom_bar(aes(x=q0029, fill=q0014), position = "fill") + 
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "top") 

p2.3.2 + labs(title ="How much have you heard about the #MeToo movement?", x = "Education Level", y = "Response Composition") + scale_fill_brewer(palette ="Set1")
```
